Q1: Are lake and terrestrial primary productivity coherent?

### 2019-12-10 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
q2 updates in progress

library(aqts)
library(wsyn)
library(rgdal)
library(LAGOSNE)
library(raster)
library(MuMIn)
library(dplyr)
library(nlme)
library(lmerTest)
library(viridis)
library(fields)
#library(partykit)
library(pdp)
library(party)
library(spatstat)
library(caret)
library(mgcv)

@@

# image(accndvi)
# points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])

@@

analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1
# analysislakes$lakedata<-analysislakes$lakedata[!analysislakes$lakeinfo$tslength < 20]
# analysislakes$lakeinfo<-analysislakes$lakeinfo[!analysislakes$lakeinfo$tslength < 20,]

@@

coh.chlaXaccndvi<-NULL
#coh.chlaXmaxndvi<-NULL

for(lind in 1:length(analysislakes$lakedata)){
  lakedat.ii<-cleandat(analysislakes$lakedata[[lind]], as.numeric(colnames(analysislakes$lakedata[[lind]])), clev=5)$cdat
  chlaXaccndvi<-coh(lakedat.ii[1,], lakedat.ii[2,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
                    norm="powall", sigmethod="fast", nrand=10000)
#  chlaXmaxndvi<-coh(lakedat.ii[1,], lakedat.ii[3,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
#                    norm="powall", sigmethod="fast", nrand=10000)
  for(rind in 1:nrow(tsranges)){
    chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
    #chlaXmaxndvi<-bandtest.coh(chlaXmaxndvi, tsranges[rind,])
  }
  coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
#  coh.chlaXmaxndvi<-rbind(coh.chlaXmaxndvi, c(t(as.matrix(chlaXmaxndvi$bandp[,3:5]))))

}

coh.chlaXaccndvi<-as.data.frame(coh.chlaXaccndvi)
#coh.chlaXmaxndvi<-as.data.frame(coh.chlaXmaxndvi)

colnames(coh.chlaXaccndvi)<-paste0("accndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))
#colnames(coh.chlaXmaxndvi)<-paste0("maxndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))

coh.chlaXaccndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid
#coh.chlaXmaxndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid

@@

```{r pedagogical example, echo=TRUE, cache=FALSE}
#looking for especially coherent lakes did not return easy-to-interpret examples. Proceeding with simulated data

@@

```{r summarize coherences, echo=TRUE, cache=FALSE}
#short timescales
hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Accumulated NDVI, short timescales", xlab="Coherence", ylab="Frequency")
#hist(coh.chlaXmaxndvi$maxndvicoh.ts1, main="Maximum NDVI, short timescales", xlab="Coherence", ylab="Frequency")

quantile(coh.chlaXaccndvi$accndvicoh.ts1)
#quantile(coh.chlaXmaxndvi$maxndvicoh.ts1)

alpha=0.05
sum(coh.chlaXaccndvi$accndvip.ts1<alpha)/nrow(coh.chlaXaccndvi)
#sum(coh.chlaXmaxndvi$maxndvip.ts1<alpha)/nrow(coh.chlaXmaxndvi)

@@

# print(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<alpha]/pi) #only pattern is that lakes don't lead the landscape
# print(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<alpha]/pi)

phicls<-c(-1,-.75,-0.25,0.25,0.75,1)

# hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian",
     breaks=seq(0,2*pi,length.out=16))
#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

#long timescales
hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Accumulated NDVI, long timescales", xlab="Coherence", ylab="Frequency")
#hist(coh.chlaXmaxndvi$maxndvicoh.ts2, main="Maximum NDVI, long timescales", xlab="Coherence", ylab="Frequency")

quantile(coh.chlaXaccndvi$accndvicoh.ts2)
#quantile(coh.chlaXmaxndvi$maxndvicoh.ts2)

alpha=0.05
sum(coh.chlaXaccndvi$accndvip.ts2<alpha)/nrow(coh.chlaXaccndvi)
#sum(coh.chlaXmaxndvi$maxndvip.ts2<alpha)/nrow(coh.chlaXmaxndvi)

print(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<alpha]/pi)
#print(coh.chlaXmaxndvi$maxndviphi.ts2[coh.chlaXmaxndvi$maxndvip.ts2<alpha]/pi)

# hist(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian",
     breaks=seq(0,2*pi,length.out=16))

#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions_20191031.tif", units="in",
     res=300, width=6.5, height=6.5)

@@

states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
lagosstates<-states[states@data$STATE %in% getstates,]

plot(lagosstates, main="Lakes selected for analysis")
points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=16, cex=1, col="blue")

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_coherencemap.tif", units="in",
     res=300, width=6.5, height=7.5)

@@

#remove any variables that don't vary in this dataset
# for(nn in 1:ncol(preds)){
#   print(colnames(preds)[nn])
#   print(unique(preds[,nn]))
# }

@@

# modvars.conn<-left_join(pred.conn, coh.chlaXaccndvi, by="lagoslakeid")
# modvars.chag<-left_join(pred.chag, coh.chlaXaccndvi, by="lagoslakeid")

@@

for(nn in 1:ncol(preds)){

  if(is.factor(preds[,nn])){
    preds[,nn]<-factor(preds[,nn])
  }

}

@@

varimp.coh.st<-varimp(cf.cohst)
print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
#hist(predcoh.st)
#hist(modvars.accndvi$accndvicoh.ts1)
predcoh.st<-predict(cf.cohst, newdata=rfdat.cohst,type="response")
# plot(predcoh.st, rfdat.cohst$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
#      xlim=c(0,1), ylim=c(0,1))
# abline(a=0,b=1)
cor.test(predcoh.st,rfdat.cohst$accndvicoh.ts1)

@@

gam.cohst<-gam(accndvicoh.ts1 ~ s(cv.accndvi) + hu8_zoneid + s(hu12_dep_totaln_tavg_mean) +
               s(hu12_nlcd2011_pct_90) + s(hu12_nlcd2011_pct_95), data=rfdat.cohst, gamma=1, weights=lwgt)
gam.check(gam.cohst)
concurvity(gam.cohst)
summary(gam.cohst)
plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))

@@

varimp.coh.lt<-varimp(cf.cohlt)
print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
#hist(predcoh.st)
#hist(modvars.accndvi$accndvicoh.ts1)
predcoh.lt<-predict(cf.cohlt, newdata=rfdat.cohlt,type="response")
# plot(predcoh.lt, rfdat.cohlt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long ts",
#      xlim=c(0,1), ylim=c(0,1))
# abline(a=0,b=1)
cor.test(predcoh.lt,rfdat.cohlt$accndvicoh.ts2)

@@

gam.cohlt<-gam(accndvicoh.ts2 ~ hu8_zoneid + s(hu12_nlcd2011_pct_52) + s(cv.accndvi) + 
                 s(wlconnections_forestedwetlands_shoreline_km) + 
                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean), data=rfdat.cohlt, gamma=1, weights=lwgt)
gam.check(gam.cohlt)
concurvity(gam.cohlt)
summary(gam.cohlt)
plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))

@@

cf.phist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))

varimp.phi.st<-varimp(cf.phist)
print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10])
predphi.st<-predict(cf.phist, newdata=rfdat.phist,type="response")
cor.test(predphi.st,cos(rfdat.phist$accndviphi.ts1))

@@

gam.phist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
                 s(buffer500m_streamdensity_headwaters_density_mperha) + 
                 s(chla), 
               data=rfdat.phist, gamma=1, weights=lwgt)
gam.check(gam.phist)
concurvity(gam.phist)
summary(gam.phist)
plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.phist, rfdat.phist))

@@

cf.philt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))

varimp.phi.lt<-varimp(cf.philt)
print(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10])
predphi.lt<-predict(cf.philt, newdata=rfdat.philt,type="response")
cor.test(predphi.lt,cos(rfdat.philt$accndviphi.ts2))

@@

gam.philt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_tri_mean) + 
                 s(hu12_nlcd2011_pct_41), 
               data=rfdat.philt, gamma=1, weights=lwgt)
gam.check(gam.philt)
concurvity(gam.philt)
summary(gam.philt)
plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.philt, rfdat.philt))

@@

```{r roughGAMplotting, echo=TRUE, cache=FALSE}

# plot(gam.cohst, main="coherence, short")
# plot(gam.cohlt, main="coherence, long")
# plot(gam.phist, main="cos(phase), short")
# plot(gam.philt, main="cos(phase), long")

```
```{r plot varimp}

@@

print(varimp.phi.st[order(varimp.phi.st, decreasing = T)][1:10])
ltxt.phist<-c("open wetlands shoreline","headwaters density","mean chlorophyll-a","stream density",
              "open wetlands contrib. area","% developed open space","nitrate deposition", "road density",
              "% developed low intensity","all wetlands contrib. area")

print(varimp.phi.lt[order(varimp.phi.lt, decreasing = T)][1:10])
ltxt.philt<-c("HUC-4 subregion","HUC-6 basin","slope","topographic roughness","% deciduous forest","% woody wetlands",
               "headwaters density","total N deposition","HUC-8 sub-basin","stream density")

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10.tif",units="in",res=300,width=6.5, height=6.5)

par(mfrow=c(2,2), mar=c(5,11,1,1), cex.main=0.9, cex.axis=0.9)

barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="Short timescale coher.", horiz=T)

barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="Long timescale coher.", horiz=T)

barplot(rev(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.phist),las=2,main="Short timescale phase", horiz=T)

barplot(rev(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.philt),las=2,main="Long timescale phase", horiz=T)

@@

mar1<-c(3,1.5,0.5,1)
#mar2<-c(2.5,1.5,1,1)
fudge=1/40

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits.tif",units="in",res=300,width=6.5, height=6.5)

par(mfrow=c(4,5),mgp=c(1.5,0.5,0),oma=c(0,2.5,0,0),mar=mar1)

plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
plot(NA,NA,xlab="HUC-8 sub-basin",xlim=c(0,1),ylim=c(0,1))
plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")

plot(gam.phist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
plot(gam.phist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
plot(gam.phist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
plot.new()
plot.new()

plot(NA,NA,xlab="HUC-8 sub-basin",xlim=c(0,1),ylim=c(0,1))
plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))

plot(NA,NA,xlab="HUC-4 subregion",xlim=c(0,1),ylim=c(0,1),ylab="long phase")
plot(gam.philt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="slope",ylab="")
plot(gam.philt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% deciduous forest",ylab="")

mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
mtext("cos(long phase)",2,at=1/8+fudge,outer=T,line=0,cex=0.7)
mtext("long coherence)",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
mtext("cos(short phase)",2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)

>>>>

library(aqts)
library(wsyn)
library(rgdal)
library(rgeos)
library(LAGOSNE)
library(raster)
library(MuMIn)
library(dplyr)
library(nlme)
library(lmerTest)
library(viridis)
library(fields)
#library(partykit)
#library(pdp)
library(png)
library(party)
library(spatstat)
library(caret)
library(mgcv)

@@

@@

analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1

@@

coh.chlaXaccndvi<-NULL

for(lind in 1:length(analysislakes$lakedata)){
  lakedat.ii<-cleandat(analysislakes$lakedata[[lind]], as.numeric(colnames(analysislakes$lakedata[[lind]])), clev=5)$cdat
  chlaXaccndvi<-coh(lakedat.ii[1,], lakedat.ii[2,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
                    norm="powall", sigmethod="fast", nrand=10000)
  for(rind in 1:nrow(tsranges)){
    chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
  }
  coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
}

coh.chlaXaccndvi<-as.data.frame(coh.chlaXaccndvi)

colnames(coh.chlaXaccndvi)<-paste0("accndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))

coh.chlaXaccndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid

@@

```{r export coherent lakes, echo=FALSE, cache=FALSE}

coherentlakes.st<-analysislakes
coherentlakes.st$lakeinfo<-coherentlakes.st$lakeinfo[coherentlakes.st$lakeinfo$lagoslakeid %in%
                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts1<0.05],]
coherentlakes.st$lakedata<-coherentlakes.st$lakedata[names(coherentlakes.st$lakedata) %in%
                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts1<0.05]]

coherentlakes.lt<-analysislakes
coherentlakes.lt$lakeinfo<-coherentlakes.lt$lakeinfo[coherentlakes.lt$lakeinfo$lagoslakeid %in%
                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts2<0.05],]
coherentlakes.lt$lakedata<-coherentlakes.lt$lakedata[names(coherentlakes.lt$lakedata) %in%
                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts2<0.05]]

save(list=c("coherentlakes.st","coherentlakes.lt"),
     file="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes.RData")

```{r pedagogical example, echo=TRUE, cache=FALSE}

@@

```{r summarize coherences, echo=TRUE, cache=FALSE}
#short timescales
quantile(coh.chlaXaccndvi$accndvicoh.ts1)

alpha=0.05
sum(coh.chlaXaccndvi$accndvip.ts1<alpha)/nrow(coh.chlaXaccndvi)

@@

#long timescales
quantile(coh.chlaXaccndvi$accndvicoh.ts2)

alpha=0.05
sum(coh.chlaXaccndvi$accndvip.ts2<alpha)/nrow(coh.chlaXaccndvi)

print(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<alpha]/pi)

#plotting
tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions_20191031.tif", units="in",
     res=300, width=6.5, height=6.5)

@@

states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020_nolakes.shp")
getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
lagosstates<-states[states@data$STATE %in% getstates,]

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map.tif",units="in",
     res=300, width=3.25, height=2.75)
par(mar=rep(0,4))
plot(lagosstates, main="",bty="o")
points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.45, col="black",bg="grey")
legend("bottomright",pch=c(0,21),col="black",pt.bg="grey",legend=c("States in LAGOS-NE","Selected lakes"),inset=c(0.025,0.01),bty="n")
dev.off()

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_coherencemap.tif", units="in",
     res=300, width=6.5, height=7.5)

@@

conpreds<-preds[,sapply(preds, is.numeric)]
cor.conpreds<-cor(conpreds,use="pairwise.complete.obs")

@@

@@

for(nn in 1:ncol(preds)){
  if(is.factor(preds[,nn])){
    preds[,nn]<-factor(preds[,nn])
  }
}

#write.csv(colnames(preds),file="~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/predictorlist.csv")

@@

varimp.coh.st<-varimp(cf.cohst)
print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
predcoh.st<-predict(cf.cohst, newdata=rfdat.cohst,type="response")
cor.test(predcoh.st,rfdat.cohst$accndvicoh.ts1)

@@

gam.cohst<-gam(accndvicoh.ts1 ~ s(cv.accndvi) + hu8_zoneid + s(hu12_dep_totaln_tavg_mean) +
               s(hu12_nlcd2011_pct_90) + s(hu12_nlcd2011_pct_95), data=rfdat.cohst, gamma=1, weights=lwgt)
gam.check(gam.cohst)
concurvity(gam.cohst,full=F)$estimate
summary(gam.cohst)
plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))

@@

varimp.coh.lt<-varimp(cf.cohlt)
print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
predcoh.lt<-predict(cf.cohlt, newdata=rfdat.cohlt,type="response")
cor.test(predcoh.lt,rfdat.cohlt$accndvicoh.ts2)

@@

gam.cohlt<-gam(accndvicoh.ts2 ~ hu8_zoneid + s(hu12_nlcd2011_pct_52) + s(cv.accndvi) + 
                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + 
                 s(wlconnections_allwetlands_contributing_area_ha), data=rfdat.cohlt, gamma=1, weights=lwgt)
gam.check(gam.cohlt)
concurvity(gam.cohlt,full=F)$estimate
summary(gam.cohlt)
plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))

@@

#cosine
cf.cosphist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
varimp.cosphi.st<-varimp(cf.cosphist)
print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10])
pred.cosphi.st<-predict(cf.cosphist, newdata=rfdat.phist,type="response")
cor.test(pred.cosphi.st,cos(rfdat.phist$accndviphi.ts1))

#sine
cf.sinphist<-party::cforest(sin(accndviphi.ts1) ~ ., data=rfdat.phist, 
                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
varimp.sinphi.st<-varimp(cf.sinphist)
print(varimp.sinphi.st[order(varimp.sinphi.st, decreasing=T)][1:10])
pred.sinphi.st<-predict(cf.sinphist, newdata=rfdat.phist,type="response")
cor.test(pred.sinphi.st,sin(rfdat.phist$accndviphi.ts1))

@@

#cosine
gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
                 s(buffer500m_streamdensity_headwaters_density_mperha) + 
                 s(chla), 
               data=rfdat.phist, gamma=1, weights=lwgt)
gam.check(gam.cosphist)
concurvity(gam.cosphist, full=F)$estimate
summary(gam.cosphist)
plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))

#sine -- ignored in main text
gam.sinphist<-gam(sin(accndviphi.ts1) ~ s(buffer500m_streamdensity_headwaters_density_mperha) + 
                 s(hu12_dep_so4_tavg_mean) + 
                 s(hu12_damdensity_pointspersqkm), 
               data=rfdat.phist, gamma=1, weights=lwgt)
gam.check(gam.sinphist)
concurvity(gam.sinphist,full=F)$estimate
summary(gam.sinphist)
plot(sin(rfdat.phist$accndviphi.ts1), predict(gam.sinphist, rfdat.phist))

@@

#cosine
cf.cosphilt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))

varimp.cosphi.lt<-varimp(cf.cosphilt)
print(varimp.cosphi.lt[order(varimp.cosphi.lt, decreasing=T)][1:10])
pred.cosphi.lt<-predict(cf.cosphilt, newdata=rfdat.philt,type="response")
cor.test(pred.cosphi.lt,cos(rfdat.philt$accndviphi.ts2))

#sine
cf.sinphilt<-party::cforest(sin(accndviphi.ts2) ~ ., data=rfdat.philt,
                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))

varimp.sinphi.lt<-varimp(cf.sinphilt)
print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10])
pred.sinphi.lt<-predict(cf.sinphilt, newdata=rfdat.philt,type="response")
cor.test(pred.sinphi.lt,sin(rfdat.philt$accndviphi.ts2))

@@

#cosine
gam.cosphilt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_slope_mean) + 
                 s(hu12_nlcd2011_pct_90), 
               data=rfdat.philt, gamma=1, weights=lwgt)
gam.check(gam.cosphilt)
concurvity(gam.cosphilt,full=F)$estimate
summary(gam.cosphilt)
plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.cosphilt, rfdat.philt))

#sine
gam.sinphilt<-gam(sin(accndviphi.ts2) ~ hu4_zoneid + s(hu12_nlcd2011_pct_82) + 
                 s(hu12_nlcd2011_pct_21), 
               data=rfdat.philt, gamma=1, weights=lwgt)
gam.check(gam.sinphilt)
concurvity(gam.sinphilt,full=F)$estimate
summary(gam.sinphilt)
plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))

@@

```{r saveResults, echo=TRUE, cache=FALSE}
# save.image(file="~/Box Sync/NSF EAGER Synchrony/Data/results_20191106.RData")
```

```{r plot varimp}

@@

print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing = T)][1:10])
ltxt.cosphist<-c("open wetlands shoreline","headwaters density","stream density","mean chlorophyll-a",
              "% developed open space","open wetlands contrib. area","all wetlands contrib. area", "road density","nitrate deposition",
              "% pasture/hay")

print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing = T)][1:10])
ltxt.sinphilt<-c("HUC-4 subregion","HUC-6 basin","% cultivated crops","HUC-8 sub-basin","% developed open space",
                 "open wetlands contrib. area","all wetlands contrib. area","% open water","all wetlands shoreline","shrub wetladns contrib. area")

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10.tif",units="in",res=300,width=6.5, height=5)

par(mfrow=c(2,2), mar=c(4,11,1,1), cex.main=0.9, cex.axis=0.9)

barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="a) Short timescale coher.", horiz=T,font.main=1)

barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="c) Long timescale coher.", horiz=T, font.main=1)

barplot(rev(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.cosphist),las=2,
        main=expression(paste("b) Short timescale cosine(",phi,")",sep="")), horiz=T)

barplot(rev(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.sinphilt),las=2,
        main=expression(paste("d) Long timescale sine(",phi,")",sep="")), horiz=T)

@@

## Make geographic variation images 
huc4_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/HU4.shp")
huc8_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/HU8.shp")

cohst_huc8<-data.frame(ZoneID=names(gam.cohst$coefficients)[grepl("hu8_zoneid",names(gam.cohst$coefficients))],
                      coeff=gam.cohst$coefficients[grepl("hu8_zoneid",names(gam.cohst$coefficients))])
rownames(cohst_huc8)<-c()
cohst_huc8$ZoneID<-substring(cohst_huc8$ZoneID,11)

cohlt_huc8<-data.frame(ZoneID=names(gam.cohlt$coefficients)[grepl("hu8_zoneid",names(gam.cohlt$coefficients))],
                      coeff=gam.cohlt$coefficients[grepl("hu8_zoneid",names(gam.cohlt$coefficients))])
rownames(cohlt_huc8)<-c()
cohlt_huc8$ZoneID<-substring(cohlt_huc8$ZoneID,11)

sinphilt_huc4<-data.frame(ZoneID=names(gam.sinphilt$coefficients)[grepl("hu4_zoneid",names(gam.sinphilt$coefficients))],
                      coeff=gam.sinphilt$coefficients[grepl("hu4_zoneid",names(gam.sinphilt$coefficients))])
rownames(sinphilt_huc4)<-c()
sinphilt_huc4$ZoneID<-substring(sinphilt_huc4$ZoneID,11)

# lagosstates_outline<-lagosstates
# lagosstates_outline@data$dissolve<-rep(1,length(lagosstates_outline))
# lagosstates_outline<-gUnaryUnion(lagosstates_outline,id=lagosstates_outline@data$dissolve)
# huc4_bdys<-raster::intersect(huc4_bdys,lagosstates_outline)
# huc8_bdys<-raster::intersect(huc8_bdys,lagosstates_outline)

# huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
# huc_codes<-huc_codes[huc_codes$hu4_zoneid %in% analysislakes$lakeinfo$hu4_zoneid,]

huc_bdys_cohst<-huc8_bdys[huc8_bdys$ZoneID %in% cohst_huc8$ZoneID,]
huc_bdys_cohst@data<-left_join(huc_bdys_cohst@data, cohst_huc8)

huc_bdys_cohlt<-huc8_bdys[huc8_bdys$ZoneID %in% cohlt_huc8$ZoneID,]
huc_bdys_cohlt@data<-left_join(huc_bdys_cohlt@data, cohlt_huc8)

huc_bdys_sinphilt<-huc4_bdys[huc4_bdys$ZoneID %in% sinphilt_huc4$ZoneID,]
huc_bdys_sinphilt@data<-left_join(huc_bdys_sinphilt@data, sinphilt_huc4)

scale1_100<-function(x){
  x1<-x-min(x)+1/100
  x1<-round(x1/max(x1)*100)
  return(x1)
}
#make smaller images that we can insert into the main figure

bight=6.5
bigwd=6.5

lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))

# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst.png", units="in",
#      res=300, width=bigwd/5, height=bight/4)
# par(mar=c(0,0,2,0))
# plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),lwd=0.5)
# lines(lagosstates_prj,lwd=0.5)
# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex=0.5)
# dev.off()
# 
# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt.png", units="in",
#      res=300, width=bigwd/5, height=bight/4)
# par(mar=c(0,0,2,0))
